Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-21 paper-2023-acsos-pulverization.tex
typos, punctuations, language, conciseness, clarity

The runtime bases its operation on three main components:
the \texttt{Spawner}, which is responsible for executing the components;
the \texttt{UnitReconfigurator}, which is responsible for reconfiguring the \emph{deployment unit}
according to the \texttt{ReconfigurationEvent}
and the \texttt{Communicator}s,
which are used to establish the components' intra-communication.
%
To start, the \texttt{PulverisationRuntime} needs to know the name of the \emph{logical device},
the \emph{host} on which it is running, and the configurations produced by the two \ac{dsl}s.
%
At the start of the system, the runtime,
based on the provided configuration,
spawns all the components that must start on the \emph{deployment unit}.
%
Similarly, the \texttt{UnitReconfigurator} starts observing all the configured \texttt{ReconfigurationEvent}s
and registers the listeners for incoming reconfigurations.
%
Each spawned component starts to execute its logic and shares data with other component via the \texttt{Communicator},
which is responsible for the components' intra-communication by leveraging the communication protocol.
%
When a reconfiguration occurs, the \texttt{UnitReconfigurator} takes into account the new deployment configuration,
by interacting with the \texttt{Spawner}, to start or stop the required components.

>>>>

The runtime bases its operation on three main components:
the \texttt{Spawner}, which is responsible for executing the components;
the \texttt{UnitReconfigurator}, which is responsible for reconfiguring the \emph{deployment unit}
according to the \texttt{ReconfigurationEvent}
and the \texttt{Communicator}s,
which are used to establish the components' intra-communication.
%
To start, the \texttt{PulverisationRuntime} needs to know the name of the \emph{logical device},
the \emph{host} on which it is running, and the configurations produced by the two \ac{dsl}s.
%
At the start of the system, the runtime,
based on the provided configuration,
spawns all the components that must start on the \emph{deployment unit}.
%
Similarly, the \texttt{UnitReconfigurator} starts observing all the configured \texttt{ReconfigurationEvent}s
and registers the listeners for incoming reconfigurations.
%
Then,
each spawned component starts
executing its logic and sharing data with other components via the \texttt{Communicator},
which is responsible for the components' intra-communication by leveraging the communication protocol.
%
Finally,
when a reconfiguration occurs, the \texttt{UnitReconfigurator} considers the new deployment configuration and,
by interacting with the \texttt{Spawner},
starts or stops components in order to achieve the new setup.
